meta-analysis

### 2018-03-21 Code/4_combined-meta-regression.Rmd
added summary plots

cod_decomp_results <- cod_decomp_results %>% rename(fitted.RE = .fitted, fixed.from.RE = .fixed, resid.RE = .resid)
```

>>>>

cod_decomp_results <- cod_decomp_results %>% rename(fitted.RE = .fitted, 
                                                    fixed.from.RE = .fixed, 
                                                    resid.RE = .resid)

cod_decomp_results <- cod_decomp_results %>% 
  mutate(national.from.RE = fitted.RE - RE.estimates, #the national trend
         residual.RE = COD_cont_yrs_mean - national.from.RE) #the difference between the observed state trends and the national trend
```
